---
title: "."
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    logo: transparent_logo_small_2.png
    
---
<style>                     
.navbar {
  background-color:#2A254B;
  #border-color:white;
}
.navbar-brand {
color:#2A254B!important;
}
.main-header.logo {
  padding: 250px 250px;
}
</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(ggmap)

# Read in the data
data <- read.csv('final_data.csv')

# set Color Values
red_color <- "#D46C4E"
orange_color <- "#F9AD6A"
yellow_color <- "#F9E07F"
green_color <- "#43978D"
blue_color <- "#264D59"
```

Clubhouse Benchmarks {data-icon="ion-android-home"}
===
Row {data-width=150}
-----------------------------------------------------------------------

### Total Recent Cases

```{r}
recent_cases <- tail(data$Weekly.Cases, n=1)

if(recent_cases>=500){
  valueBox(value = round(recent_cases,0),icon = "ion-medkit",caption = "Phase: 0, Virtual Clubhouse", color = red_color)
} else if (recent_cases<500 & recent_cases>=250) {
  valueBox(value = round(recent_cases,0),icon = "ion-medkit",caption = "Phase: 1, Outdoor without Crowds", color = orange_color)
} else if (recent_cases<250 & recent_cases>=100) {
  valueBox(value = round(recent_cases,0),icon = "ion-medkit",caption = "Phase: 2, Outdoor with Crowds", color = yellow_color)
} else if (recent_cases<100 & recent_cases>=50) {
  valueBox(value = round(recent_cases,0),icon = "ion-medkit",caption = "Phase: 3, Indoor with Masks", color = green_color)
} else {
  valueBox(value = recent_cases,icon = "ion-medkit",caption = "Phase: 4", color = blue_color)}
```

### Total Recent Cases

```{r}
recent_pos = tail(data$Average.Cases, n=1)

if(recent_pos>=70){
  valueBox(value = round(recent_pos,0),icon = "ion-person-add",caption = "Phase: 0, Virtual Clubhouse", color = red_color)
} else if (recent_pos<70 & recent_pos>=50) {
  valueBox(value = round(recent_pos,0),icon = "ion-person-add",caption = "Phase: 1, Outdoor without Crowds", color = orange_color)
} else if (recent_pos<50 & recent_pos>=30) {
  valueBox(value = round(recent_pos,0),icon = "ion-person-add",caption = "Phase: 2, Outdoor with Crowds", color = yellow_color)
} else if (recent_pos<30 & recent_pos>=10) {
  valueBox(value = round(recent_pos,0),icon = "ion-person-add",caption = "Phase: 3, Indoor with Masks", color = green_color)
} else {
  valueBox(value = round(recent_pos,0),icon = "ion-person-add",caption = "Phase: 4, Indoor (masks optional)", color = blue_color)}
```

### Total Hospitalizations

```{r}
recent_hosp = tail(data$Weekly.Hospitalizations, n=1)

if(recent_hosp>=40){
  valueBox(value = round(recent_hosp,0),icon = "ion-heart",caption = "Phase: 0, Virtual Clubhouse", color = red_color)
} else if (recent_hosp<40 & recent_hosp>=25) {
  valueBox(value = round(recent_hosp,0),icon = "ion-heart",caption = "Phase: 1, Outdoor without Crowds", color = orange_color)
} else if (recent_hosp<25 & recent_hosp>=15) {
  valueBox(value = round(recent_hosp,0),icon = "ion-heart",caption = "Phase: 2, Outdoor with Crowds", color = yellow_color)
} else if (recent_hosp<15 & recent_hosp>=5) {
  valueBox(value = round(recent_hosp,0),icon = "ion-heart",caption = "Phase: 3, Indoor with Masks", color = green_color)
} else {
  valueBox(value = round(recent_hosp,0),icon = "ion-heart",caption = "Phase: 4, Indoor (masks optional)", color = blue_color)}
```

### New Confirmed Deaths

```{r}
recent_deaths = tail(data$Weekly.Deaths, n=1)

if(recent_deaths>=10){
  valueBox(value = round(recent_deaths,0),icon = "ion-ios-pulse-strong",caption = "Phase: 0, Virtual Clubhouse", color = red_color)
} else if (recent_deaths<10 & recent_deaths>=5) {
  valueBox(value = round(recent_deaths,0),icon = "ion-ios-pulse-strong",caption = "Phase: 1, Outdoor without Crowds", color = orange_color)
} else if (recent_deaths<5 & recent_deaths>=3) {
  valueBox(value = round(recent_deaths,0),icon = "ion-ios-pulse-strong",caption = "Phase: 2, Outdoor with Crowds", color = yellow_color)
} else if (recent_deaths<3 & recent_deaths>=2) {
  valueBox(value = round(recent_deaths,0),icon = "ion-ios-pulse-strong",caption = "Phase: 3, Indoor with Masks", color = green_color)
} else {
  valueBox(value = round(recent_deaths,0),icon = "ion-ios-pulse-strong",caption = "Phase: 4, Indoor (masks optional)", color = blue_color)}
```

Row
-----------------------------------------------------------------------

### New Confirmed COVID-19 Cases
```{r}
data$Date <- as.Date(data$Date)

fig_cases <- plot_ly(data, x = ~Date, y = ~Weekly.Cases, type = 'scatter', mode = 'lines')
fig_cases <- layout(fig_cases,
              xaxis = list(title = '', showgrid = FALSE),
              yaxis = list(title = '', showgrid = FALSE),
              shapes = list(
                list(type = "rect",
                     fillcolor = red_color, line = list(color = red_color), opacity = 0.3,
                     x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                     y0 = 500, y1 = max(data$Weekly.Cases), yref = "y"),
                list(type = "rect",
                     fillcolor = orange_color, line = list(color = orange_color), opacity = 0.2,
                     x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                     y0 = 250, y1 = 500, yref = "y"),
                list(type = "rect",
                     fillcolor = yellow_color, line = list(color = yellow_color), opacity = 0.2,
                     x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                     y0 = 100, y1 = 250, yref = "y"),
                list(type = "rect",
                     fillcolor = green_color, line = list(color = green_color), opacity = 0.2,
                     x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                     y0 = 50, y1 = 100, yref = "y"),
                list(type = "rect",
                     fillcolor = blue_color, line = list(color = blue_color), opacity = 0.2,
                     x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                     y0 = 0, y1 = 50, yref = "y")))
fig_cases
```

### Positive COVID-19 Test Results
```{r}
data$Date <- as.Date(data$Date)

fig_tests <- plot_ly(data, x = ~Date, y = ~Average.Cases, type = 'scatter', mode = 'lines')
fig_tests <- layout(fig_tests,
                    xaxis = list(title = '', showgrid = FALSE),
                    yaxis = list(title = '', showgrid = FALSE),
                    shapes = list(
                      list(type = "rect",
                           fillcolor = red_color, line = list(color = red_color), opacity = 0.3,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = 70, y1 = max(data$Average.Cases), yref = "y"),
                      list(type = "rect",
                           fillcolor = orange_color, line = list(color = orange_color), opacity = 0.2,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = 50, y1 = 70, yref = "y"),
                      list(type = "rect",
                           fillcolor = yellow_color, line = list(color = yellow_color), opacity = 0.2,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = 30, y1 = 50, yref = "y"),
                      list(type = "rect",
                           fillcolor = green_color, line = list(color = green_color), opacity = 0.2,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = 10, y1 = 30, yref = "y"),
                      list(type = "rect",
                           fillcolor = blue_color, line = list(color = blue_color), opacity = 0.2,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = 0, y1 = 10, yref = "y")))
fig_tests
```

### New COVID-19 Hospital Admissions
```{r}
data$Date <- as.Date(data$Date)

fig_hospitals <- plot_ly(data, x = ~Date, y = ~Weekly.Hospitalizations, type = 'scatter', mode = 'lines')
fig_hospitals <- layout(fig_hospitals,
                    xaxis = list(title = '', showgrid = FALSE),
                    yaxis = list(title = '', showgrid = FALSE),
                    shapes = list(
                      list(type = "rect",
                           fillcolor = red_color, line = list(color = red_color), opacity = 0.3,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = 40, y1 = max(data$Weekly.Hospitalizations), yref = "y"),
                      list(type = "rect",
                           fillcolor = orange_color, line = list(color = orange_color), opacity = 0.2,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = 25, y1 = 40, yref = "y"),
                      list(type = "rect",
                           fillcolor = yellow_color, line = list(color = yellow_color), opacity = 0.2,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = 15, y1 = 25, yref = "y"),
                      list(type = "rect",
                           fillcolor = green_color, line = list(color = green_color), opacity = 0.2,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = 5, y1 = 15, yref = "y"),
                      list(type = "rect",
                           fillcolor = blue_color, line = list(color = blue_color), opacity = 0.2,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = 0, y1 = 5, yref = "y")))
fig_hospitals
```

### New Confirmed COVID-19 Deaths
```{r}
data$Date <- as.Date(data$Date)

fig_deaths <- plot_ly(data, x = ~Date, y = ~Weekly.Deaths, type = 'scatter', mode = 'lines')
fig_deaths <- layout(fig_deaths,
                        xaxis = list(title = '', showgrid = FALSE),
                        yaxis = list(title = '', showgrid = FALSE),
                        shapes = list(
                          list(type = "rect",
                               fillcolor = red_color, line = list(color = red_color), opacity = 0.3,
                               x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                               y0 = 10, y1 = max(data$Weekly.Deaths), yref = "y"),
                          list(type = "rect",
                               fillcolor = orange_color, line = list(color = orange_color), opacity = 0.2,
                               x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                               y0 = 5, y1 = 10, yref = "y"),
                          list(type = "rect",
                               fillcolor = yellow_color, line = list(color = yellow_color), opacity = 0.2,
                               x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                               y0 = 3, y1 = 5, yref = "y"),
                          list(type = "rect",
                               fillcolor = green_color, line = list(color = green_color), opacity = 0.2,
                               x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                               y0 = 2, y1 = 3, yref = "y"),
                          list(type = "rect",
                               fillcolor = blue_color, line = list(color = blue_color), opacity = 0.2,
                               x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                               y0 = 0, y1 = 2, yref = "y")))
fig_deaths
```

State Benchmarks {data-icon="ion-android-globe"}
===
Row {data-width=350}
-----------------------------------------------------------------------

### Daily Cases per Million

```{r}
daily_cases <- round(tail(data$Avg.Cases.MI, n=1),0)

if(daily_cases>=70){
  valueBox(value = daily_cases,icon = "ion-medkit",caption = "Risk Threshold: D, Virtual Clubhouse", color = red_color)
} else if (daily_cases<70 & daily_cases>=40) {
  valueBox(value = daily_cases,icon = "ion-medkit",caption = "Risk Threshold: C, Outdoor with Crowds", color = orange_color)
} else if (daily_cases<40 & daily_cases>=20) {
  valueBox(value = daily_cases,icon = "ion-medkit",caption = "Risk Threshold: B, Outdoor without Crowds", color = yellow_color)
} else if (daily_cases<20 & daily_cases>=7) {
  valueBox(value = daily_cases,icon = "ion-medkit",caption = "Risk Threshold: A, Indoor with Masks", color = green_color)
} else {
  valueBox(value = daily_cases,icon = "ion-medkit",caption = "Risk Threshold: Low, Indoor (masks optional)", color = blue_color)}
```

### Daily Positive Test Rate Percentage

```{r}
daily_pos <- round(tail(data$Avg.Positives.Rate, n=1),2)
daily_pos_noround <- tail(data$Avg.Positives.Rate, n=1)

if(daily_pos_noround>=.15){
  valueBox(value = daily_pos,icon = "ion-person-add",caption = "Risk Threshold: D, Virtual Clubhouse", color = red_color)
} else if (daily_pos_noround<.15 & daily_pos_noround>=.10) {
  valueBox(value = daily_pos,icon = "ion-person-add",caption = "Risk Threshold: C, Outdoor without Crowds", color = orange_color)
} else if (daily_pos_noround<.10 & daily_pos_noround>=.07) {
  valueBox(value = daily_pos,icon = "ion-person-add",caption = "Risk Threshold: B, Outdoor with Crowds", color = yellow_color)
} else if (daily_pos_noround<.07 & daily_pos_noround>=.03) {
  valueBox(value = daily_pos,icon = "ion-person-add",caption = "Risk Threshold: A, Indoor with Masks", color = green_color)
} else {
  valueBox(value = daily_pos,icon = "ion-person-add",caption = "Risk Threshold: Low, Indoor (masks optional)", color = blue_color)}
```

Row
-----------------------------------------------------------------------

### Daily Cases per Million
```{r}
data$Date <- as.Date(data$Date)

fig_cases_mi <- plot_ly(data, x = ~Date, y = ~Avg.Cases.MI, type = 'scatter', mode = 'lines')
fig_cases_mi <- layout(fig_cases_mi,
              xaxis = list(title = '', showgrid = FALSE),
              yaxis = list(title = '', showgrid = FALSE),
              shapes = list(
                list(type = "rect",
                     fillcolor = red_color, line = list(color = red_color), opacity = 0.3,
                     x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                     y0 = 70, y1 = max(data$Avg.Cases.MI), yref = "y"),
                list(type = "rect",
                     fillcolor = orange_color, line = list(color = orange_color), opacity = 0.2,
                     x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                     y0 = 40, y1 = 70, yref = "y"),
                list(type = "rect",
                     fillcolor = yellow_color, line = list(color = yellow_color), opacity = 0.2,
                     x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                     y0 = 20, y1 = 40, yref = "y"),
                list(type = "rect",
                     fillcolor = green_color, line = list(color = green_color), opacity = 0.2,
                     x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                     y0 = 7, y1 = 20, yref = "y"),
                list(type = "rect",
                     fillcolor = blue_color, line = list(color = blue_color), opacity = 0.2,
                     x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                     y0 = 0, y1 = 7, yref = "y")))
fig_cases_mi
```

### Daily Positive Test Rate
```{r}
data$Date <- as.Date(data$Date)

fig_pos_mi <- plot_ly(data, x = ~Date, y = ~Avg.Positives.Rate, type = 'scatter', mode = 'lines')
fig_pos_mi <- layout(fig_pos_mi,
                    xaxis = list(title = '', showgrid = FALSE),
                    yaxis = list(title = '', showgrid = FALSE),
                    shapes = list(
                      list(type = "rect",
                           fillcolor = red_color, line = list(color = red_color), opacity = 0.3,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = .15, y1 = max(data$Avg.Positives.Rate), yref = "y"),
                      list(type = "rect",
                           fillcolor = orange_color, line = list(color = orange_color), opacity = 0.2,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = .10, y1 = .15, yref = "y"),
                      list(type = "rect",
                           fillcolor = yellow_color, line = list(color = yellow_color), opacity = 0.2,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = .07, y1 = .10, yref = "y"),
                      list(type = "rect",
                           fillcolor = green_color, line = list(color = green_color), opacity = 0.2,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = .03, y1 = .07, yref = "y"),
                      list(type = "rect",
                           fillcolor = blue_color, line = list(color = blue_color), opacity = 0.2,
                           x0 = head(data$Date, n=1), x1 = tail(data$Date, n=1), xref = "x",
                           y0 = 0, y1 = .03, yref = "y")))
fig_pos_mi
```